Implicit yaddayadda

### 2011-09-20 papers/PLDI2012/implicitization.tex
algorithme

We distinguish two phases when analysing a point $p_i \in P_R$:
\begin{enumerate}
\item We search for paths starting at point $p_i$, such that these paths are in
$P$, i.e are included in the working subgraph. Each time we find a path, we
update the abstract value of the destination point of the path. This is the
phase explained in \ref{subsec:ascending}.
\item  When the precedent phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). However, there may
exist such paths in the entire multigraph, that are not in $P$. The second phase
computes these paths and adds them to $P'$.
\end{enumerate}

@@

\section{Disjunctive invariants}
\label{sec:disjunctive}

>>>>

We distinguish two phases when analysing a point $p_i \in P_R$:
\begin{enumerate}
\item We search for paths starting at point $p_i$, such that these paths are in
$P$, i.e are included in the working subgraph. Each time we find a path, we
update the abstract value of the destination point of the path. This is the
phase explained in \ref{subsec:ascending}.
\item  When the previous phase terminates, there is no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). However, there may
exist such paths in the entire multigraph, that are not in $P$. The second phase
computes these paths and adds them to $P'$. We also use SMT solving to discover
these new paths, but we slightly change the SMT formula given to the SMT solver.
We now simply check for the satisfiability of $f(p_i)$ instead of $f(p_i) \wedge
P$. Since we already know that $f(p_i) \wedge P$ is \emph{unsatisfiable}, all
the paths given by the SMT solver won't be in $P$.
\end{enumerate}

@@

Termination of this algorihm is guaranteed, because:
\begin{itemize}
\item 
the subset of paths $P$ is
strictly increasing at each loop iteration, and bounded by the finite set of
paths in the entire graph. 
\item the set $P'$ always verifies $P \wedge P' = false$ by construction, 
which guarantees that $P$
will eventually be empty after a finite number of loop iterations.
\end{itemize}
\section{Disjunctive invariants}
\label{sec:disjunctive}
